\documentclass{article}

\author{Alchemist}

\title{Alternative AT Domination System}

\begin{document}
\maketitle

\section{Design Principle}
\begin{itemize}
	\item The consequential event like loosing a city should take a long time (months).
	\item One type of style (pvp,pve,social) should not be advantaged.
	\item The system should not affect too much people that don't want to be part of it.
	\item The system should be easy to extend and the maximum number of AT event should be tied to it.
	\item Attacking multiple cities at once should be very difficult.
\end{itemize}

\section{Definitions}
\begin{description}
	\item[City:] A city/town that is currently owned by a player.
	\item[Faction:] A player controlled faction.
	\item[Leader:] The leader of a faction.
	\item[Capital:] The main city of the faction.
	\item[Controlled City] Other city controlled by the faction and with a governor as it head.
	\item[Governor:] The leader of controlled city, is appointed by the controlling faction leader.
	\item[Resources:] Abstract quantity representing the resources in men, money and equipment of a city.
\end{description}

\section{Resources}
The core principle of the idea is the notion of resources. It is a commodity that can be seen as a representation of the strength of a city. Resources are gained by te activity of the faction and spend for the maintenance of the city and waging war.

The following ways can be used to obtain resources:
\begin{itemize}
	\item The number of member of the faction bring a quantity of resource.
	\item Population of player active inside a city.
	\item An official player event bring resources to the organising city proportional to the affluence of the event.
	\item DM event can add resources.
	\item Treaties with other cities like protectorat or help shipment allows to receive resources transferred from another city. 
\end{itemize}

The resource can be lost in the following manner:
\begin{itemize}
	\item A DM event like demon attack destroying part of a city.
	\item War.
	\item Treaties with other cities forcing you to send resources.
	\item A montly maintenance fee, higher in case of many protectorat and possessions.
\end{itemize}

\section{War}

A war has the following rules:
\begin{itemize}
	\item A war happen between two cities.
	\item The war is declared by the governor of the city with approval of the faction leader if needed.
	\item Once a war is declared, each side need to decide a quantity of resources to dedicate to the war.
	\item When the dedicated resource of one side reach zero. The enemy army march toward the city and will attain the city in one RL week.
	\item The war is done by participating in automatic event of different kind but with balanced team. This is done on a separated map not in the city itself. Possibilities are:
		\begin{itemize}
			\item Team pvp with some npc.
			\item Capture the flag.
			\item Team against npc.
		\end{itemize}
		Each win of one side remove point to the other side proportional to the difference of resources.
	\item Participating in event may allow player to get reward.
	\item Multiple war between different cities are possible and are treated independently.
\end{itemize}

\section{Discussion of the System}
The interesting part of the system is that it give something to do to all kind of players and give them an utility in the full system.
\begin{itemize}
	\item Social player and event organizer together with builder help their cities by attracting player which increase the resource that can be used for war.
	\item Pvper and Pveer can play with other like minded person.
	\item And finally the effect of dm event can be noticeable by the bonus or malus resources received.
	\item Inactive cities will automatically disappear because of the upkeep cost.
	\item Faction waging war to everybody will not survive except strong economy because of the need to diversify their resources. 
	\item The majority of system needed are already in place. Like the war event for CTF for example.
\end{itemize}

\section{Step to Implement}
\begin{itemize}
	\item Add a variable to the database for the resource of all cities.
	\item Add dm mean to manipulate the variable.
	\item Make automatic the war event by adapting CTF.
	\item Have statistics tool to know how many player are actif in all cities.
	\item Balance the gain and lost of resources given the different features.
\end{itemize}

\end{document}